### 2022-02-22 documentos/intro.tex
salvaguardando

\ddnote{Yo agregare un parrafo delineando la literatura alrededor de Ruskai}
Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
\newline
{\blue [Aqui arranco con la introduccion]\\}
Similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space. For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real numbers which are not fully independent (the complete positivity condition imposes which regions have physical meaning, see Ref.~\cite{zimansbook}). Therefore, even the qubit case is difficult to explore, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}. Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations. For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}. For general finite-dimensional channels, families of channels defined as convex combinations of quantum-classical channels, in turn defined with bases that belong to a mutually unbiased basis (MUB), are studied in Ref.~\cite{nathanson2007pauli}. These channels have properties in common with unital qubit channels [...].  Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020}
\par
[Role of completely positivity]
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps}
% }}}

>>>>

\ddnote{Yo agregare un parrafo delineando la literatura alrededor de Ruskai}
Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
\newline
{\blue [Aqui arranco con la introduccion]\\}
Similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space. For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real numbers which are not fully independent (the complete positivity condition imposes which regions have physical meaning, see Ref.~\cite{zimansbook}). Therefore, even the qubit case is difficult to explore, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}. Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations. For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}. For general finite-dimensional channels, families of channels defined as convex combinations of quantum-classical channels, in turn defined with bases that belong to a mutually unbiased basis (MUB), are studied in Ref.~\cite{nathanson2007pauli}. These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs. Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020} as another attempt to generalize unital qubit channels.
%
[Other references]

\par
In the present work, we give a generalization of the qubit flip operations (bit, phase and bit-phase) to the 
[Role of completely positivity]
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps}
% }}}
